---
title: "Cell-Cell Communication Figure With commfigR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cell-Cell Communication Figure With commfigR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, message=FALSE}
library(commfigR)
library(ncfigR)
```

```{r, fig.width=10, fig.height=9}
lr <- readr::read_tsv(system.file("extdata/lr_pairs.tsv", package = "commfigR"), show_col_types = FALSE)
scores <- readr::read_tsv(system.file("extdata/communication_scores.tsv", package = "commfigR"), show_col_types = FALSE)
diff <- readr::read_tsv(system.file("extdata/differential_lr.tsv", package = "commfigR"), show_col_types = FALSE)
edges <- readr::read_tsv(system.file("extdata/network_edges.tsv", package = "commfigR"), show_col_types = FALSE)

fig <- compose_communication_figure(lr, scores, diff, edges)
fig
```

## Condition-separated overview

The bundled tables are synthetic demonstrations. Scores are summarized
separately by condition; display limits do not remove rows from the summaries.

```{r, fig.width=7.2, fig.height=8.7}
overview <- compose_communication_overview(lr, top_n = 6, data.out = TRUE)
overview$plot
```

`overview$data$display` and `overview$data$network_edges` hold the exact
displayed values. `overview$data$edges` and `overview$data$totals` retain all
supplied interactions. Missing exported interactions are absent, not measured
zeros. These descriptive score differences are not donor-level tests.

For a traceable Agent task use `scripts/run_comm_job.R` from the repository.
Rendering success remains `needs_review`; inspect PNG and vector artwork before
submitting the six-check review through `scripts/review_comm_job.R`.
