---
title: "Existing Spatial Results With spfigR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Existing Spatial Results With spfigR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, message=FALSE}
library(spfigR)
library(ncfigR)
```

## Section-aware overview

Declare coordinate units, axis direction and expression scale. The synthetic
example below contains repeated spot IDs in two sections and explicit zeros.
Each section is plotted separately. Composition counts supplied spots, not cells.

```{r overview, fig.width=7, fig.height=7}
coordinates <- readr::read_tsv(system.file("extdata/overview_coordinates.tsv", package = "spfigR"),
  col_types = readr::cols(spot_id = readr::col_character()))
values <- readr::read_tsv(system.file("extdata/overview_features.tsv", package = "spfigR"),
  col_types = readr::cols(spot_id = readr::col_character()))
compose_spatial_overview(coordinates, values, expression_scale = "log_normalized",
  coordinate_unit = "arbitrary", y_axis = "up", point_size = 2)
```

Use `run_sp_job()` for frozen inputs, export checks and a reviewable report.
Technical success is `needs_review`; `review_sp_job()` records actual PNG and
vector inspection. Neither entry point validates histology alignment or spatial
association statistics.

## Legacy direct panels

These functions accept their own panel tables. Use the section-aware overview
for multi-section tasks rather than merging coordinates into legacy panels.

```{r}
coords <- readr::read_tsv(system.file("extdata/spatial_coordinates.tsv", package = "spfigR"), show_col_types = FALSE)
features <- readr::read_tsv(system.file("extdata/spatial_features.tsv", package = "spfigR"), show_col_types = FALSE)
composition <- readr::read_tsv(system.file("extdata/spatial_composition.tsv", package = "spfigR"), show_col_types = FALSE)
regions <- readr::read_tsv(system.file("extdata/spatial_zoom_regions.tsv", package = "spfigR"), show_col_types = FALSE)
palette <- read_nc_palette(system.file("extdata/domain_palette.tsv", package = "spfigR"))

fig <- compose_spatial_niche_figure(coords, features, composition, regions, palette = palette)
fig
```
